---
title: "cross_validation"
author: "Yuning Wang"
date: "11/12/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(mgcv)

set.seed(1)
```

Creat a non-linear model

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```


## Training and testing

```{r}
train_df = sample_frac(nonlin_df, size = .8)

test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

## Fit three models of varying goodness

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Let's look at some fits.

```{r}
# The linear_mod
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

# Smooth model
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")

# Wiggly model
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + geom_point() + 
  geom_line(aes(y = pred), color = "red")
```

## Try to do cross validation

The root mean square error. Pick the model do better on the testing dataset, which means the rmse value is lower.

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

## Do this all using 'modelr'

```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 
```

one note about resample

```{r}
# cv_df %>% pull(train) %>% .[[1]] %>% as_tibble
# turn all of them into datasets
cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Try fitting the linear model to all of these datasets

```{r}
cv_results = cv_df %>% 
  mutate(
    linear_mods = map(.x = train, ~lm(y ~ x, data = .x)),
    smooth_mods = map(.x = train, ~gam(y ~ s(x), data = .x)),
    wiggly_mod  = map(train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x)),
    
    rmse_lin = map2_dbl(.x = linear_mods, .y = test, ~rmse(.x, .y)),
    rmse_smo = map2_dbl(.x = smooth_mods, .y = test, ~rmse(.x, .y)),
    rmse_wiggly = map2_dbl(wiggly_mod, test, ~rmse(model = .x, data = .y))
  )
```

visualization

```{r}
cv_results %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

## Example

```{r}
child_growth = read_csv("./data/nepalese_children.csv")

child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```

Add change point term

```{r}
child_growth =
  child_growth %>% 
  mutate(weight_cp = (weight > 7) * (weight - 7))
```

```{r}
linear_mod = lm(armc ~ weight, data = child_growth)
pwl_mod    = lm(armc ~ weight + weight_cp, data = child_growth)
smooth_mod = gam(armc ~ s(weight), data = child_growth)
```

Fit models

```{r}
child_growth %>% 
  gather_predictions(linear_mod, pwl_mod, smooth_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5) +
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(~model)
```

Use CV 

```{r}
cv_df =
  crossv_mc(child_growth, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

repeat

```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
         pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
         smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
         rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

Draw a plot

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Because of the interpretation, it's better to choose pwl at this case







